Security vs. Maintainability: Fixing Vulnerabilities Obfuscates your Code

### 2019-01-23 paper/ICPC19/icpc19.tex
paper
paper running
abstract --> sofia, add numbers and review

\documentclass[10pt,conference]{IEEEtran} 
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage[table,xcdraw]{xcolor}
\usepackage{xcolor}
\definecolor{mypink3}{cmyk}{0, 0.7808, 0.4429, 0.1412}

@@

\title{Security vs. Maintainability: Fixing Vulnerabilities Obfuscates your Code\\
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{abstract}

Lorem Ipsum is simply dummy text of the printing and typesetting industry. 
Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, 
when an unknown printer took a galley of type and scrambled it to make a type 
specimen book. It has survived not only five centuries, but also the leap into 
electronic typesetting, remaining essentially unchanged. It was popularised in 
the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, 
and more recently with desktop publishing software like Aldus PageMaker including 
versions of Lorem Ipsum. It was popularised in the 1960s with the release of 
Letraset sheets containing Lorem Ipsum passages, and more recently with desktop 
publishing software like Aldus PageMaker including versions of Lorem Ipsum.

\end{abstract}

@@

Add a point for motivation with one of the examples of the poster.

@@

\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.5\textwidth]{figures/maintainability.pdf}
 	\caption{Maintainability difference for security and baseline commits \textcolor{mypink3}{@update}}
\end{figure}

@@

{
  \bibliography{paper}
}

>>>>

\documentclass[10pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage[table,xcdraw]{xcolor}
\usepackage{framed}
\usepackage{xcolor}
\definecolor{mypink3}{cmyk}{0, 0.7808, 0.4429, 0.1412}

@@

\title{Security vs. Maintainability: Fixing Vulnerabilities Obfuscates your Code%\\
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{abstract}
  Security is a crucial non-functionality requirement for software applications.
  However, building secure software is far from trivial as developers lack both
  the knowledge and tools to effectively address this concern. In this paper, we
  study the impact of changes to improve security on the maintainability of several
  open source applications. Using a dataset containing XXX security-oriented
  commits, we measure maintainability --- as computed by the Software Improvement
  Group's web-based source code analysis service \emph{Better Code Hub} (BCH) ---
  before and after the security refactoring. Results show that making software
  more secure comes at a cost on  maintainability. This is particularly evident
  in refactorings to deal with \emph{XXX} and \emph{YYY} attacks.
  Furthermore, we have found evidence that security-related changes are more
  likely to be modified in the future than regular code changes.
\end{abstract}

@@

\begin{framed}
\textit{\textbf{RQ1} What is the impact }
\end{framed}

@@

\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.4\textwidth]{figures/maintainability.pdf}
 	\caption{Maintainability difference for security and baseline commits \textcolor{mypink3}{@update}}
\end{figure}

\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.55\textwidth]{figures/category.pdf}
 	\caption{Maintainability difference by type of security commit \textcolor{mypink3}{@update}}
\end{figure}

\cite{Wang:2008:DSJ:1330017.1330021}

@@

{
 \bibliographystyle{IEEEtran}
  \bibliography{icpc19}
}
